A quantitative framework for investigating the reliability of empirical network construction: supplemental information

### 2018-07-04 manuscript/supplemental.tex
fine-tuned attribution table

  \begin{table}
  \caption{Attributions for silhouette images taken from PhyloPic.org and used in Figure 1 (\emph{main text}). Terms for the CC BY-NC-SA 3.0 license can be found at \emph{https://creativecommons.org/licenses/by-nc-sa/3.0/}. Terms for the CC BY 3.0 license can be found at \emph{https://creativecommons.org/licenses/by/3.0/}.}
  \begin{tabular}{l|ll}
  Image & PhyloPic taxon & Attribution \\
  \hline
  Lion & Panthera leo & Public domain (uncredited) \\
  Leopard & Panthera pardus & Lukasiniho (CC BY-NC-SA 3.0; image not changed) \\
  Jackal & Canidae & Brian Gratwicke (photo) and T. Michael Keesey (vectorization). (CC BY 3.0; image not changed) \\
  Elephant & Loxodonta africana & Jan A. Venter, Herbert H. T. Prins, David A. Balfour & Rob Slotow (vectorized by T. Michael Keesey) (CC BY 3.0; image not changed) \\
  Zebra & Equus quagga & Cathy (CC BY-NC-SA 3.0; image not changed) \\
  Impala & Aepyceros melampus & Public domain (unknown author) \\
  Hare & Leporidae & Sarah Werning (CC A 3.0; image not changed) \\
  Acacia & Acacia tree & Mattia Menchetti (public domain) \\
  Grass & \multicolumn{2}{c}{Not sourced from PhyloPic. Public domain.} \\
  \hline
  \end{tabular}
  \end{table}

>>>>

  \begin{table}
  \caption{Attributions for silhouette images taken from PhyloPic.org and used in Figure 1 (\emph{main text}). Terms for the CC BY-NC-SA 3.0 license can be found at \emph{https://creativecommons.org/licenses/by-nc-sa/3.0/}. Terms for the CC BY 3.0 license can be found at \emph{https://creativecommons.org/licenses/by/3.0/}.}
  \begin{tabular}{l|l m{10cm}}
  Image & PhyloPic taxon & Attribution \\
  \hline
  Lion & Panthera leo & Public domain (uncredited) \\
  Leopard & Panthera pardus & Lukasiniho (CC BY-NC-SA 3.0; image not changed) \\
  Jackal & Canidae & Brian Gratwicke (photo) and T. Michael Keesey (vectorization). (CC BY 3.0; image not changed) \\
  Elephant & Loxodonta africana & Jan A. Venter, Herbert H. T. Prins, David A. Balfour \& Rob Slotow (vectorized by T. Michael Keesey) (CC BY 3.0; image not changed) \\
  Zebra & Equus quagga & Cathy (CC BY-NC-SA 3.0; image not changed) \\
  Impala & Aepyceros melampus & Public domain (unknown author) \\
  Hare & Leporidae & Sarah Werning (CC A 3.0; image not changed) \\
  Acacia & Acacia & Mattia Menchetti (public domain) \\
  Grass & & Not sourced from PhyloPic. Public domain. \\
  \hline
  \end{tabular}
  \end{table}
